---
title: "Who Is That? Perceptual Expertise on Other-Race Face Comparisons, Disguised Face Comparisons, and Face Memory - Analysis Script"
author: "Amy N. Yates, Jacqueline G. Cavazos, Géraldine Jeckeln, Ying Hu, Eilidh Noyes, Carina A. Hahn, Alice J. O'Toole, P. Jonathon Phillips"
date: "2023-05-08"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, message=FALSE}
# This is the analysis script for the paper "Who Is That? Perceptual Expertise on Other-Race Face Comparisons, Disguised Face Comparisons, and Face Memory"
#  The paper can be found at https://doi.org/10.31234/osf.io/s87na

# Update these to your local file paths
nist.ore.file<-"NIST/ORE.csv"
nist.disguise.file<-"NIST/Disguise.csv"
nist.cfmt.file<-"NIST/CFMT.csv"

utd.ore.file<-"UTD/ORE.csv"
utd.disguise.file<-"UTD/Disguise.csv"
utd.cfmt.file<-"UTD/CFMT.csv"


knitr::opts_chunk$set(echo = FALSE, comment = NA)

library(GGally)
library(knitr)
library(kableExtra)
library(rlang)
library(tidyverse)
```

```{r constants}
# For plots
medShape<-16
medSize<-5
medStroke<-0.5
medColor<-"red"

# For chunks
figWidth<-7
figWideWidth<-9
figAlign<-"center"

numSigDigits<-3
yLim<-c(0.3, 1.0)

titleSize<-20
textSize<-16

# Colorblind-friendly palette from:
#     http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/
cbPalette<-c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442",
             "#0072B2", "#D55E00", "#CC79A7", "#000000")

creColors<-cbPalette[c(2, 6)]

disTasks<-c("Non-Disguised", "Impersonation", "Evasion")
```

```{r functions, message=FALSE}
as_dataFrame_withCols<-function(rObj, colNames, ...)
{
  colnames(rObj)<-colNames
  rDF<-as.data.frame(rObj, ...)
  return(rDF)
}

# Calculate AUC using Mann-Whitney U/Wilcoxon rank sum test
auc<-function(posScores, negScores)
{
  posScores<-posScores[!is.na(posScores)]
  negScores<-negScores[!is.na(negScores)]
  numPos<-length(posScores)
  numNeg<-length(negScores)
  
  wResults<-suppressWarnings(wilcox.test(posScores, negScores))
  grabAUC<-unname(wResults$statistic/(numPos*numNeg))
  
  return(grabAUC)
}

# Create stat table
stat_table<-function(dataFrame, groupCol, scoreCol)
{
  theGroups<-dataFrame %>% pull({{groupCol}}) %>% unique()
  numGroups<-length(theGroups)
  numPairs<-choose(numGroups, 2)
  
  thePairs<-combn(theGroups, 2) %>%
    t() %>%
    as_dataFrame_withCols(colNames=c("Group1", "Group2")) %>%
    mutate(N1=integer(numPairs),
           N2=integer(numPairs),
           Median1=numeric(numPairs),
           Median2=numeric(numPairs),
           UValue=numeric(numPairs),
           pValue=numeric(numPairs),
           alpha=0.05/numPairs)
  
  for (i in 1:numPairs)
  {
    gp1<-thePairs$Group1[i]
    gp2<-thePairs$Group2[i]
    
    scores1<-dataFrame %>%
      filter({{groupCol}}==gp1) %>%
      pull({{scoreCol}})
    
    scores2<-dataFrame %>%
      filter({{groupCol}}==gp2) %>%
      pull({{scoreCol}})
    
    n1<-length(scores1)
    n2<-length(scores2)
    
    wilTest<-suppressWarnings(wilcox.test(x=scores1, y=scores2))
    
    u1<-wilTest$statistic
    u2<-n1*n2 - u1
    
    thePairs$N1[i]<-n1
    thePairs$N2[i]<-n2
    thePairs$Median1[i]<-median(scores1)
    thePairs$Median2[i]<-median(scores2)
    thePairs$UValue[i]<-min(u1, u2)
    thePairs$pValue[i]<-wilTest$p.value
  }
  
  thePairs<-thePairs %>%
    mutate(BonP=p.adjust(p=pValue, method="bonferroni"))
  
  return(thePairs)
}

pair_table<-function(dataFrame, idCols, groupCol, scoreCol)
{
  theGroups<-dataFrame %>% pull({{groupCol}}) %>% unique() %>% as.character()
  numGroups<-length(theGroups)
  numPairs<-choose(numGroups, 2)
  
  wideData<-dataFrame %>%
    pivot_wider(id_cols={{idCols}}, names_from={{groupCol}},
                values_from={{scoreCol}})
  
  thePairs<-combn(theGroups, 2) %>%
    t() %>%
    as_dataFrame_withCols(colNames=c("Group1", "Group2")) %>%
    mutate(N=integer(numPairs),
           Median1=numeric(numPairs),
           Median2=numeric(numPairs),
           WValue=numeric(numPairs),
           pValue=numeric(numPairs),
           alpha=0.05/numPairs)
  
  for (i in 1:numPairs)
  {
    gp1<-thePairs$Group1[i]
    gp2<-thePairs$Group2[i]
    
    scores1<-wideData %>%
      pull(gp1)
    
    scores2<-wideData %>%
      pull(gp2)
    
    n<-length(scores1)
    
    wilTest<-suppressWarnings(wilcox.test(x=scores1, y=scores2, paired=TRUE))
    
    t1<-wilTest$statistic
    t2<-choose(n+1, 2) - t1
    
    thePairs$N[i]<-n
    thePairs$Median1[i]<-median(scores1)
    thePairs$Median2[i]<-median(scores2)
    thePairs$WValue[i]<-min(t1, t2)
    thePairs$pValue[i]<-wilTest$p.value
  }
  
  thePairs<-thePairs %>%
    mutate(BonP=p.adjust(p=pValue, method="bonferroni"))
  
  return(thePairs)
}
```

```{r split violin plot}
# Code in this chunk by Stack Overflow user jan-glx, found at: 
# https://stackoverflow.com/questions/35717353/split-violin-plot-with-ggplot2

GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
  grp <- data[1, "group"]
  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])

  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
      1))
    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
    aesthetics$alpha <- rep(1, nrow(quantiles))
    both <- cbind(quantiles, aesthetics)
    quantile_grob <- GeomPath$draw_panel(both, ...)
    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
  }
  else {
    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
  }
})

geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
                              show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}
```

```{r nist data}
# Read in data
nist.ore.df<-read.csv(file=nist.ore.file, stringsAsFactors=FALSE)
nist.dis.df<-read.csv(file=nist.disguise.file, stringsAsFactors=FALSE)
nist.cfmt.df<-read.csv(file=nist.cfmt.file, stringsAsFactors=FALSE)

# Calculate AUC for each participant - ORE
nist.ore.auc<-nist.ore.df %>%
  spread(mateBinary, Scores) %>% 
  group_by(SubID, Group, Stim_Race) %>%
  summarize(AUC=auc(posScores=`1`, negScores=`0`), .groups="drop")

# Calculate AUC for each participant - Disguise
# Non-Disguised Condition
nist.dis_non.auc<-nist.dis.df %>%
  filter(Type %in% c("1A", "2A")) %>%
  spread(mateBinary, Scores) %>% 
  group_by(SubID, Group) %>%
  summarize(AUC=auc(posScores=`1`, negScores=`0`), .groups="drop") %>%
  mutate(Task="Non-Disguised")

# Impersonation Condition
nist.dis_imp.auc<-nist.dis.df %>%
  filter(Type %in% c("1A", "2B")) %>%
  spread(mateBinary, Scores) %>% 
  group_by(SubID, Group) %>%
  summarize(AUC=auc(posScores=`1`, negScores=`0`), .groups="drop") %>%
  mutate(Task="Impersonation")

# Evasion Condition
nist.dis_eva.auc<-nist.dis.df %>%
  filter(Type %in% c("1B", "2A")) %>%
  spread(mateBinary, Scores) %>% 
  group_by(SubID, Group) %>%
  summarize(AUC=auc(posScores=`1`, negScores=`0`), .groups="drop") %>%
  mutate(Task="Evasion")

# Together
nist.dis.auc<-rbind(nist.dis_non.auc, nist.dis_imp.auc, nist.dis_eva.auc)

# Calculate Percent Correct (PC) for each participant
nist.cfmt.pc<-nist.cfmt.df %>%
  group_by(SubID, Group) %>%
  summarize(PC=mean(Correct), .groups="drop")
```

```{r utd data}
# Read in data
utd.ore.df<-read.csv(file=utd.ore.file, stringsAsFactors=FALSE)
utd.dis.df<-read.csv(file=utd.disguise.file, stringsAsFactors=FALSE)
utd.cfmt.df<-read.csv(file=utd.cfmt.file, stringsAsFactors=FALSE)

# Calculate AUC for each participant - ORE
utd.ore.auc<-utd.ore.df %>%
  spread(mateBinary, Scores) %>% 
  group_by(SubID, Group, Stim_Race) %>%
  summarize(AUC=auc(posScores=`1`, negScores=`0`), .groups="drop")

# Calculate AUC for each participant - Disguise
# Non-Disguised Condition
utd.dis_non.auc<-utd.dis.df %>%
  filter(Type %in% c("1A", "2A")) %>%
  spread(mateBinary, Scores) %>% 
  group_by(SubID, Group) %>%
  summarize(AUC=auc(posScores=`1`, negScores=`0`), .groups="drop") %>%
  mutate(Task="Non-Disguised")

# Impersonation Condition
utd.dis_imp.auc<-utd.dis.df %>%
  filter(Type %in% c("1A", "2B")) %>%
  spread(mateBinary, Scores) %>% 
  group_by(SubID, Group) %>%
  summarize(AUC=auc(posScores=`1`, negScores=`0`), .groups="drop") %>%
  mutate(Task="Impersonation")

# Evasion Condition
utd.dis_eva.auc<-utd.dis.df %>%
  filter(Type %in% c("1B", "2A")) %>%
  spread(mateBinary, Scores) %>% 
  group_by(SubID, Group) %>%
  summarize(AUC=auc(posScores=`1`, negScores=`0`), .groups="drop") %>%
  mutate(Task="Evasion")

# Together
utd.dis.auc<-rbind(utd.dis_non.auc, utd.dis_imp.auc, utd.dis_eva.auc)

# Calculate Percent Correct (PC) for each participant
utd.cfmt.pc<-utd.cfmt.df %>%
  group_by(SubID, Group) %>%
  summarize(PC=mean(Correct), .groups="drop")
```

```{r combine}
ore.auc<-rbind(nist.ore.auc, utd.ore.auc)
dis.auc<-rbind(nist.dis.auc, utd.dis.auc) %>%
  mutate(Task=factor(Task, levels=disTasks))
cfmt.pc<-rbind(nist.cfmt.pc, utd.cfmt.pc)
```

## Other-Race Face Identification

```{r ore split violin plot, fig.align=figAlign, fig.width=figWidth}
ggplot(ore.auc, aes(Group, AUC, fill=Stim_Race)) +
  geom_split_violin() +
  stat_summary(fun=median, geom="point", size=medSize, stroke=medStroke,
               mapping=aes(shape=Stim_Race, fill=Stim_Race)) +
  coord_cartesian(ylim=yLim) +
  scale_shape_manual(values=c(21, 24),
                     labels=c("Caucasian", "East Asian")) +
  scale_fill_manual(values=creColors,
                    labels=c("Caucasian", "East Asian")) +
  scale_x_discrete(breaks=c("Examiners", "Reviewers",
                            "Students_Caucasian",
                            "Students_EastAsian"),
                   labels=c("Examiners", "Reviewers",
                            "Caucasian\nStudents", "East Asian\nStudents")) +
  labs(x="Group", shape="Race of Stimuli", fill="Race of Stimuli")
```

### Causasian Stimuli across Groups

```{r ore ca stim mw tests, warning=FALSE}
stat_table(ore.auc %>% filter(Stim_Race=="Caucasian"), Group, AUC)  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Group 1", "Group 2", "$N_1$", "$N_2$",
                    "Median 1", "Median 2", "$U$", "$p$", "$\\alpha$",
                    "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

### East Asian Stimuli across Groups

```{r ore ea stim mw tests, warning=FALSE}
stat_table(ore.auc %>% filter(Stim_Race=="EastAsian"), Group, AUC)  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Group 1", "Group 2", "$N_1$", "$N_2$",
                    "Median 1", "Median 2", "$U$", "$p$", "$\\alpha$",
                    "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

### Groups across Stimuli Sets

```{r ore across stimuli sets}
wide.ore.auc<-ore.auc %>%
  pivot_wider(id_cols=c(Group, SubID),
              names_from=Stim_Race,
              values_from=AUC)

ore.pairs<-data.frame(Group=c("Examiners", "Reviewers",
                              "Students_Caucasian", "Students_EastAsian"),
                      N=numeric(4),
                      MedianC=numeric(4),
                      MedianEA=numeric(4),
                      WValue=numeric(4),
                      pValue=numeric(4),
                      alpha=0.05/4)
  
for (j in 1:4)
{
  gp<-ore.pairs$Group[j]
  
  scoresC<-wide.ore.auc %>%
    filter(Group==gp) %>%
    pull(Caucasian)
  
  scoresEA<-wide.ore.auc %>%
    filter(Group==gp) %>%
    pull(EastAsian)
  
  n<-length(scoresC)
  
  wilTest<-suppressWarnings(wilcox.test(x=scoresC, y=scoresEA, paired=TRUE))
  
  t1<-wilTest$statistic
  t2<-choose(n+1, 2) - t1
  
  ore.pairs$N[j]<-n
  ore.pairs$MedianC[j]<-median(scoresC)
  ore.pairs$MedianEA[j]<-median(scoresEA)
  ore.pairs$WValue[j]<-min(t1, t2)
  ore.pairs$pValue[j]<-wilTest$p.value
}

ore.pairs %>%
  mutate(BonP=p.adjust(p=pValue, method="bonferroni"))  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Group", "$N$",
                    "Median C Stim", "Median EA Stim", "$W$", "$p$",
                    "$\\alpha$", "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```


## Disguise

```{r disguise grid violin plot, fig.align=figAlign, fig.width=figWidth}
disLabs<-c(Examiners="Examiners",
           Reviewers="Reviewers",
           Students_Caucasian="Caucasian Students",
           Students_EastAsian="East Asian Students")

ggplot(dis.auc, aes(x=Task, y=AUC, fill=Task)) +
  geom_hline(yintercept=0.5) +
  geom_violin() +
  facet_wrap(~Group, labeller=labeller(Group=disLabs)) +
  stat_summary(fun=median, geom="point", size=medSize, stroke=medStroke,
               mapping=aes(shape=Task, fill=Task)) +
  scale_shape_manual(values=c(21, 24, 22), breaks=disTasks) +
  scale_fill_manual(values=cbPalette[2:4], breaks=disTasks) +
  coord_cartesian(ylim=c(0.40, 1.00)) +
  labs(x=NULL) +
  theme(axis.text.x=element_text(angle=15, vjust=1, hjust=1))
```

### Non-Disguised across Groups

```{r dis non-dis mw tests, warning=FALSE}
stat_table(dis.auc %>% filter(Task=="Non-Disguised"), Group, AUC)  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Group 1", "Group 2", "$N_1$", "$N_2$",
                    "Median 1", "Median 2", "$U$", "$p$", "$\\alpha$",
                    "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

### Impersonation across Groups

```{r dis imp mw tests, warning=FALSE}
stat_table(dis.auc %>% filter(Task=="Impersonation"), Group, AUC)  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Group 1", "Group 2", "$N_1$", "$N_2$",
                    "Median 1", "Median 2", "$U$", "$p$", "$\\alpha$",
                    "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

### Evasion across Groups

```{r dis eva mw tests, warning=FALSE}
stat_table(dis.auc %>% filter(Task=="Evasion"), Group, AUC)  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Group 1", "Group 2", "$N_1$", "$N_2$",
                    "Median 1", "Median 2", "$U$", "$p$", "$\\alpha$",
                    "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

### Examiners across Tasks

```{r dis ex mw tests, warning=FALSE}
pair_table(dis.auc %>% filter(Group=="Examiners"), idCols=SubID,
           Task, AUC)  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Condition 1", "Condition 2", "$N$",
                    "Median 1", "Median 2", "$W$", "$p$", "$\\alpha$",
                    "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

### Reviewers across Tasks

```{r dis rv mw tests, warning=FALSE}
pair_table(dis.auc %>% filter(Group=="Reviewers"), idCols=SubID,
           Task, AUC)  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Condition 1", "Condition 2", "$N$",
                    "Median 1", "Median 2", "$W$", "$p$", "$\\alpha$",
                    "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

### Caucasian Students across Tasks

```{r dis cs mw tests, warning=FALSE}
pair_table(dis.auc %>% filter(Group=="Students_Caucasian"), idCols=SubID,
           Task, AUC)  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Condition 1", "Condition 2", "$N$",
                    "Median 1", "Median 2", "$W$", "$p$", "$\\alpha$",
                    "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

### East Asian Students across Tasks

```{r dis eas mw tests, warning=FALSE}
pair_table(dis.auc %>% filter(Group=="Students_EastAsian"), idCols=SubID,
           Task, AUC)  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Condition 1", "Condition 2", "$N$",
                    "Median 1", "Median 2", "$W$", "$p$", "$\\alpha$",
                    "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

## Memory

```{r cfmt violin plot, fig.align=figAlign, fig.width=figWidth}
ggplot(cfmt.pc %>% mutate(PerCor=PC*100), aes(x=Group, y=PerCor)) +
  geom_violin() +
  stat_summary(fun=median, geom="point", shape=medShape, size=medSize,
               stroke=medStroke, color=medColor) +
  geom_dotplot(binaxis="y", stackdir="center", dotsize=1.0, binwidth=1) +
  coord_cartesian(ylim=yLim*100) +
  scale_x_discrete(breaks=c("Examiners", "Reviewers", "Students"),
                   labels=c("Examiners", "Reviewers", "Students")) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  labs(x="Group", y="Percent Correct")
```

```{r cfmt mw tests, warning=FALSE}
stat_table(cfmt.pc, Group, PC)  %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(col.names=c("Group 1", "Group 2", "$N_1$", "$N_2$",
                    "Median 1", "Median 2", "$U$", "$p$", "$\\alpha$",
                    "Bonferroni-adjusted $p$"),
        align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

## Façade/Disguise Binarized

### Positive

```{r disguise binarized positive}
dis.posBin.df<-rbind(nist.dis.df, utd.dis.df) %>%
  mutate(BinScore=if_else(Scores > 0, true=1, false=0),
         Correct=as.numeric(BinScore==mateBinary),
         Set=factor(case_when(Type=="1A" ~ "ND Match",
                       Type=="2A" ~ "ND Non-Match",
                       Type=="1B" ~ "Evasion",
                       Type=="2B" ~ "Impersonation",
                       TRUE ~ "Something's Wrong"),
                    levels=c("ND Match", "ND Non-Match",
                             "Evasion", "Impersonation")))

dis.posBin.pc<-dis.posBin.df %>%
  group_by(SubID, Group, Set) %>%
  summarize(PC=mean(Correct), .groups="drop")

dis.posBin.pc %>%
  group_by(Set, Group) %>%
  summarize(Mean=mean(PC), .groups="drop") %>%
  pivot_wider(id_cols=Set, names_from=Group, values_from=Mean) %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```

### Non-Negative

```{r disguise binarized non-negative}
dis.nonNegBin.df<-rbind(nist.dis.df, utd.dis.df) %>%
  mutate(BinScore=if_else(Scores >= 0, true=1, false=0),
         Correct=as.numeric(BinScore==mateBinary),
         Set=factor(case_when(Type=="1A" ~ "ND Match",
                       Type=="2A" ~ "ND Non-Match",
                       Type=="1B" ~ "Evasion",
                       Type=="2B" ~ "Impersonation",
                       TRUE ~ "Something's Wrong"),
                    levels=c("ND Match", "ND Non-Match",
                             "Evasion", "Impersonation")))

dis.nonNeg.pc<-dis.nonNegBin.df %>%
  group_by(SubID, Group, Set) %>%
  summarize(PC=mean(Correct), .groups="drop")

dis.nonNeg.pc %>%
  group_by(Set, Group) %>%
  summarize(Mean=mean(PC), .groups="drop") %>%
  pivot_wider(id_cols=Set, names_from=Group, values_from=Mean) %>%
  mutate_if(is.numeric, function(x) signif(x, digits=numSigDigits)) %>%
  kable(align="c", escape=FALSE) %>%
  kable_styling(full_width=FALSE)
```
